\documentclass[12pt, a1paper, landscape, margin=10mm, innermargin=15mm, blockverticalspace=15mm, colspace=15mm, subcolspace=8mm]{tikzposter}
\usepackage[utf8]{inputenc}
 
\title{A high level Schematic editor for simplified HDL Entry}
\author{Student: Lei Wang (Wilson)}
\date{June, 27th, 2019}
\institute{Imperial College London}

\usepackage{blindtext}
\usepackage{comment}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{url}

\definetitlestyle{sampletitle}{
width=500mm, roundedcorners=20, linewidth=2pt, innersep=5pt,
titletotopverticalspace=15mm, titletoblockverticalspace=15mm
}{
\begin{scope}[line width=\titlelinewidth, rounded corners=\titleroundedcorners]
\draw[color=blocktitlebgcolor, fill=titlebgcolor]
(\titleposleft,\titleposbottom) rectangle (\titleposright,\titlepostop);
\end{scope}
}
\usetitlestyle{sampletitle}

\defineblockstyle{sampleblockstyle}{
titlewidthscale=1, bodywidthscale=1,titleleft,
titleoffsetx=0pt, titleoffsety=0pt, bodyoffsetx=0mm, bodyoffsety=10mm,
bodyverticalshift=10mm, roundedcorners=5, linewidth=3pt,
titleinnersep=6mm, bodyinnersep=0.8cm
}{
\draw[color=framecolor, fill=blockbodybgcolor,
rounded corners=\blockroundedcorners] (blockbody.south west)
rectangle (blockbody.north east);
\ifBlockHasTitle
\draw[color=framecolor, fill=blocktitlebgcolor,
rounded corners=\blockroundedcorners] (blocktitle.south west)
rectangle (blocktitle.north east);
\fi
}
\useblockstyle{sampleblockstyle} 

\usepackage{tikz}
\usetikzlibrary{shapes.geometric, arrows, positioning, fit,calc}
\newcommand*\circled[1]{\tikz[baseline=(char.base)]{
            \node[shape=circle,draw,inner sep=1pt] (char) {#1};}}
 
\begin{document}


\settitle{ \centering \vbox{
\@titlegraphic \\[\TP@titlegraphictotitledistance] \centering
\color{titlefgcolor} {\bfseries \Huge \sc \@title \par}
\vspace*{1em}
{\LARGE Supervisor: Dr Thomas J.W. Clarke \par} 
\vspace*{1em}
{\LARGE \@author \par} 
\vspace*{1em}
{\LARGE \@institute \par} 
\vspace*{1em}
{\LARGE \@date \par} 
}}

\maketitle

\begin{columns}
    \column{0.33}
    \block{Abstract}    
    {The project aims to produce a piece of software that is used as a high level schematic editor for simplified HDL (Hardware Description Language) Entry by the first-year undergraduate students at Imperial College London studying digital electronics doing synchronous FPGA (Field Programmable Gate Array) digital hardware design. The software is very similar to the Visual2 project in structure of the application stack. The project itself is a combination of the third-year High Level Programming course and the first-and-second-year Digital Electronics course. The implementation involves the use of functional programming and the knowledge of Verilog.}
    
    \block{Feature}
    {
    
\begin{itemize}
    \item The software is a graphical design tool for FPGA hardware design. For creating custom logic blocks, user can either fill in truth tables to generate standalone blocks, or connect different logic blocks together to form a higher level block.
    \item The application is designed to be cross-platform, either for production use or development purposes.
    \item Although the source code is in F\#, interop with JavaScript is made possible by Fable.
\end{itemize}
    }
    
    \block{Electron Framework}
    {
\tikzstyle{block} = [rectangle, minimum width=4cm, minimum height=1cm, text centered, draw={rgb:red,0;green,102;blue,168}, fill={rgb:red,0;green,102;blue,168}, text=white]

\tikzstyle{arrow} = [thick,->,>=stealth]

\begin{tikzpicture}[node distance=3cm]

\node (nodejs) [block] {Electron};

\node (webcontent) [block, right of=nodejs, xshift=6cm] {Web content};

\node (user) [block, right of=webcontent, xshift=6cm] {User};

\node (browser) [block, below of=user] {Electron window};

\node (systemapi) [block, below of=nodejs] {System API};

\draw [arrow] (nodejs) -- (webcontent) node[midway, fill=white] {\circled{1}Deliver};

\draw [arrow] (webcontent) -- (browser) node[midway, fill=white] {\circled{2}Render and Display in};

\draw [arrow] (user) -- (browser) node[midway, fill=white] {\circled{3}React to};

\draw [arrow] (browser) -- ++ (-8, 0) node[midway, fill=white] {\circled{4}Send user response to} -- (nodejs) ; 

\draw [arrow] (nodejs) -- (systemapi) node[midway, fill=white] {\circled{5}Interact with};

\end{tikzpicture}    

Electron is built on Node.js and provides an environment to run a web-like application with access to system API. Developer writes code in HTML, CSS and JavaScript and deploys using the Electron framework.

    }
    
    \block{Application Stack}
    {
\tikzstyle{block} = [rectangle, minimum width=4cm, minimum height=1cm, text centered, draw={rgb:red,0;green,102;blue,168}, fill={rgb:red,0;green,102;blue,168}, text=white]

\tikzstyle{blockInclude} = [rectangle, minimum width=5cm, minimum height=1cm, draw=black]

\tikzstyle{blockIncludeLarge} = [rectangle, minimum width=5cm, minimum height=1cm, draw=black]

\tikzstyle{arrow} = [thick,->,>=stealth]

\begin{tikzpicture}[node distance=2cm]

\node (electronAPI) [block] {Electron API};

\node (JSLib) [block, right of=electronAPI, xshift=6cm] {JavaScript Library};

\node (fableImport) [block, below of=electronAPI] {Fable.Import};

\node (fableJsInterop) [block, below of=JSLib] {Fable.Core.JsInterop};

\node (fsharpProject) [blockInclude, below of=fableImport] {};

\node [anchor=north west] at (fsharpProject.north west) {F\# Projects};

\node (compiler) [block, right of=fsharpProject, xshift=6cm] {Fable compiler};

\node (webpack) [block, below of=compiler] {Webpack};

\node (webpackConfig) [block, right of=compiler, xshift=5cm] {Webpack configuration};

\node (js) [blockIncludeLarge, below of=webpack] {};

\node [anchor=north west] at (js.north west) {JavaScript Code};

\node (html) [blockInclude, below of=fsharpProject, yshift=-1.5cm] {};

\node [anchor=north west] at (html.north west) {HTML, CSS};

\node (electron) [block, below of=js] {Electron};

\node (browser) [block, right of=electron, xshift=3cm] {Application};

\draw [arrow] (electronAPI) -- (fableImport);

\draw [arrow] (JSLib) -- (fableJsInterop);

\draw [arrow] (fableImport) -- (fsharpProject);

\draw [arrow] (fableJsInterop) -- (fsharpProject.north east);

\draw [arrow] (fsharpProject) -- (compiler);

\draw [arrow] (compiler) -- (webpack);

\draw [arrow] (webpackConfig) |- (webpack);

\draw [arrow] (webpack) -- (js);

\draw [arrow] (html) |- (electron);

\draw [arrow] (js) -- (electron);

\draw [arrow] (electron) -- (browser);

\end{tikzpicture}

F\# is used to implement the application. However, the Electron framework accepts JavaScript hence a compiler is needed to transpile F\# to JavaScript. Fable is the chosen compiler and the output JavaScript code is bundled by webpack. Fable also allows F\# to interop with JavaScript. Therefore, using JavaScript library is made possible.

HTML and CSS is still needed for configuring and styling the GUI layout. The elements on the GUI and their styles can be changed via F\# using the \textit{Fable.Import} package.

\textit{JointJS} is the selected JavaScript library for implementing the block diagram editor.
    }
 
    \column{0.33}
    \block{Electron Processes and F\# Projects}
    {
\tikzstyle{blockInclude} = [rectangle, minimum width=22cm, minimum height=7cm, draw=black]

\tikzstyle{blockSmall} = [rectangle, minimum width=6cm, minimum height=6cm, draw=black]

\tikzstyle{block} = [rectangle, minimum width=4cm, minimum height=1cm, text centered, draw={rgb:red,0;green,102;blue,168}, fill={rgb:red,0;green,102;blue,168}, text=white]

\begin{tikzpicture}[node distance=4cm]

\node (electronapplication) [blockInclude] {};

\node [anchor=north west] at (electronapplication.north west) {Electron application};

\node [anchor=east] at (electronapplication.east) {More windows...};

\node (page1) [blockSmall, right of=electronapplication, xshift=-7cm] {};

\node [anchor=north west] at (page1.north west) {Window 1};

\node (page2) [blockSmall, right of=page1, xshift=3cm] {};

\node [anchor=north west] at (page2.north west) {Window 2};

\node (main) [block, right of=electronapplication, xshift=-12.5cm, yshift=1.5cm] {Main process};

\node (renderer1) [block, right of=main, xshift=1.5cm] {Renderer process 1};

\node (html1) [block, below of=renderer1, yshift=2.5cm] {HTML file 1};

\node (style1) [block, below of=html1, yshift=2.5cm] {Styling file 1};

\node (renderer2) [block, right of=renderer1, xshift=3cm] {Renderer process 2};

\node (html2) [block, below of=renderer2, yshift=2.5cm] {HTML file 2};

\node (style2) [block, below of=html2, yshift=2.5cm] {Styling file 2};

\end{tikzpicture}    

The application can have multiple renderer processes but only have one main process. Each process corresponds to one F\# project. The implementation has three F\# projects, \textit{Main} (correspond to the Electron main process), \textit{Renderer} (correspond to the GUI of the main window) and \textit{blockConfigureWindow} (correspond to the window for creating new blocks using truth tables).
    }
    
    \block{Application Windows}
    {
The following diagram shows the GUI of the main window. The style of the menu bar adapts to the operating system and has keyboard shortcut support.

\begin{tikzpicture}[node distance=1.5cm]

\node (window) [rectangle, minimum width=16cm, minimum height=9cm, draw=black] {};

\node [anchor=west] at (-8,4.25) {Title bar};

\node [anchor=west] at (-8,3.75) {Menu bar};

\node [anchor=west] at (-8,3.15) {Tabs};

\node [anchor=west] at (4,2.5) {Information pane};

\node [anchor=west] at (4,-1.3) {Block pane};

\node [anchor=west] at (-2.5,-1) {Canvas};

\draw (-8,4) -- (8,4);

\draw (-8,3.5) -- (8,3.5);

\draw (-8,2.8) -- (8,2.8);

\draw (4,2.8) -- (4,-4.5);

\draw (4,-1) -- (8,-1);

\end{tikzpicture}

\tikzstyle{arrow} = [thick,->,>=stealth]

The diagram below shows the window for creating basic logic blocks using truth tables. The window allows user to create blocks using truth table. To create blocks by combining other blocks, user needs to use the block diagram editor, i.e. the main window.

\begin{tikzpicture}[node distance=1.5cm][Window to add basic logic blocks]

\node (window) [rectangle, minimum width=14cm, minimum height=15cm, draw=black] {};

\node [anchor=west] at (-7,7.2) {Create new logic blocks};

\node [anchor=west] at (-7,6) {Type:};

\node (type) [rectangle, minimum width=4cm, minimum height=0.8cm, draw=black] at (-3.5,6) {};

\node (enterName) [anchor=west] at (7.5,6) {\circled{1}Enter block name};

\draw [arrow] (enterName) -- (type);

\node [anchor=west] at (-7,4.6) {Number of inputs:};

\node (enterInput) [anchor=west] at (7.5,4.6) {\circled{2}Enter number of inputs};

\node (inputNumber) [rectangle, minimum width=4cm, minimum height=0.8cm, draw=black] at (-0.8,4.6) {};

\draw [arrow] (enterInput) -- (inputNumber);

\node [anchor=west] at (-7,3.2) {Number of outputs:};

\node (outputNumber) [rectangle, minimum width=4cm, minimum height=0.8cm, draw=black] at (-0.6,3.2) {};

\node (enterOutput) [anchor=west] at (7.5,3.2) {\circled{3}Enter number of outputs};

\draw [arrow] (enterOutput) -- (outputNumber);

\draw (-7,6.9) -- (7,6.9);

\draw (-7,2.5) -- (7,2.5);

\node [anchor=west] at (-7,1.5) {in0};

\node (in0) [rectangle, minimum width=4cm, minimum height=0.8cm, draw=black] at (-4,1.5) {};

\node (namePorts) [anchor=west] at (7.5,1.5) {\circled{4}Name each port.*};

\draw [arrow] (namePorts) -- (in0);

\node [anchor=west] at (-7,0.1) {...};

\draw (-7, -0.5) -- (7,-0.5);

\node [anchor=west] at (-7, -1) {Truth table};

\node (truthTable) [rectangle, minimum width=2cm, minimum height=0.5cm, draw=black] at (-1.5,-1) {Configure truth table};

\node (truthTableButton) [anchor=west] at (7.5,-1) {\circled{5}Click to expand truth table. Fill in.};

\draw [arrow] (truthTableButton) -- (truthTable);

\draw (-7, -3.5) -- (7,-3.5);

\node [anchor=west] at (-7, -4) {Block diagram};

\node (blockView) [rectangle, minimum width=2cm, minimum height=0.5cm, draw=black] at (-1,-4) {Generate block view};

\node (truthTableButton) [anchor=west] at (7.5,-4) {\circled{6}(Optional) Click to view block shape.};

\draw [arrow] (truthTableButton) -- (blockView);

\node (OK) [rectangle, minimum width=1cm, minimum height=0.5cm, draw=black] at (3.5,-7) {OK};

\node (Cancel) [rectangle, minimum width=1cm, minimum height=0.5cm, draw=black] at (5.5,-7) {Cancel};

\node (OKClick) [anchor=west] at (7.5,-6) {\circled{7}Click to submit data.};

\draw [arrow] (OKClick) -| (OK);

\end{tikzpicture}

There is also an About window to display information on author and versions of libraries. It is not put in a separate F\# project but instead implemented using the Electron \textit{dialog.showMessageBox} API.
    }

    \column{0.33}
    \block{Application Functions}
    {
\tikzstyle{block} = [rectangle, minimum width=4cm, minimum height=1cm, text centered, draw={rgb:red,0;green,102;blue,168}, fill={rgb:red,0;green,102;blue,168}, text=white]

\tikzstyle{arrow} = [thick,->,>=stealth]

\begin{tikzpicture}[node distance=3cm]

\node (truthtable) [block] {Truth table};

\node (blocks) [block, below of=truthtable, yshift=1cm] {Buttom-level blocks};

\node (otherblocks) [block, below of=blocks, yshift=1cm] {Other high-level blocks};

\node (highlevelblocks) [block, right of=blocks, xshift=3cm] {High-level blocks};

\node (Verilog) [block, right of=highlevelblocks, xshift = 3cm, yshift=-1.5cm] {Verilog};

\node (highleveldesign) [block, above of=Verilog] {Higher-level design};

\draw [arrow] (truthtable) -- (highlevelblocks);

\draw [arrow] (blocks) -- (highlevelblocks);

\draw [arrow] (otherblocks) -- (highlevelblocks);

\draw [arrow] (highlevelblocks) -- (Verilog);

\draw [arrow] (highlevelblocks) -- (highleveldesign);

\end{tikzpicture}

User can create basic logic blocks using truth tables. Such blocks are added to the available block list and can be added to the canvas. The design in the canvas can be used to generate a single block as well. Every time a block is generated, the graphical representation of the block as well as the Verilog code of the block are saved to files. User can also save the design only without generating blocks.
    }
    
    \block{IPC}
    {
\tikzstyle{block} = [rectangle, minimum width=4cm, minimum height=1cm, text centered, draw={rgb:red,0;green,102;blue,168}, fill={rgb:red,0;green,102;blue,168}, text=white]

\tikzstyle{arrow} = [thick,->,>=stealth]

\begin{tikzpicture}[node distance=3cm]

\node (renderer) [block] {Renderer process};

\node (main) [block, right of=nodejs, xshift=6cm] {Main process};

\draw [arrow] (renderer) -- ++ (0, 1) -- ++ (7, 0) node[midway, fill=white] {IPCRenderer} -- (main) ; 

\draw [arrow] (main) -- ++ (0, -1) -- ++ (-7, 0) node[midway, fill=white] {IPCMain} -- (renderer);

\end{tikzpicture}    

\begin{tikzpicture}[node distance=3cm]

\node (renderer) [block] {Renderer process};

\node (main) [block, right of=renderer, xshift=6cm] {Main process};

\node (systemAPI) [block, right of=main, xshift=6cm] {System API};

\draw [arrow] (renderer) -- (main) node[midway, fill=white] {\circled{1}\textit{remote} call};

\draw [arrow] (main) -- ++ (0, 1) -- ++ (7, 0) node[midway, fill=white] {\circled{2}API call} -- (systemAPI);

\draw [arrow] (systemAPI) -- ++ (0, -1) -- ++ (-7, 0) node[midway, fill=white] {\circled{3}Response} -- (main);

\end{tikzpicture}
.
\begin{tikzpicture}[node distance=3cm]

\node (renderer1) [block] {Renderer process 1};

\node (main) [block, right of=renderer, xshift=6cm] {Main process};

\node (renderer2) [block, right of=main, xshift=6cm] {Renderer process 2};

\draw [arrow] (renderer1) -- (main) node[midway, fill=white] {\circled{1}\textit{IPCRenderer}};

\draw [arrow] (main) -- (renderer2) node[midway, fill=white] {\circled{2}\textit{IPCMain}};

\end{tikzpicture}

An alternative way is to replace \textit{IPCRenderer} with the \textit{Remote} module. \\

\begin{tikzpicture}[node distance=3cm]

\node (renderer1) [block] {Renderer process 1};

\node (main) [block, right of=renderer, xshift=6cm] {Main process};

\node (renderer2) [block, right of=main, xshift=6cm] {Renderer process 2};

\draw [arrow] (renderer1) -- (main) node[midway, fill=white] {\circled{1}\textit{Remote}};

\draw [arrow] (main) -- (renderer2) node[midway, fill=white] {\circled{2}\textit{IPCMain}};

\end{tikzpicture}

IPC is the abbreviation for Inter-Process Communication. In Electron, main and renderer processes are separated from each other. The main process handles system API and the renderer process handles GUI events. IPC is used when the communication between processes is needed. 

At the moment, Electron has not implemented a direct way for two renderer processes to communicate directly. Communication between renderer processes needs to be relayed by the main process. The application has multiple windows and uses IPC to pass information between those windows.

    }
    
    \block{Project Outcome}
    {
    \begin{itemize}
        \item F\# bindings for using the  \textit{JointJS} JavaScript drawing library.
        \item An application that generates Verilog for synchronous digital hardware design from a graphical design and truth tables. The code is available at \url{https://github.com/ImperialCollegeLondon/HDL_Editor}.
        \item A verification that F\# + Electron is a feasible way to implement desktop application. The desktop application combines the JavaScript ecosystem and the static typing feature of function programming together with the help of Fable.
    \end{itemize}
    }
    
    \block{Acknowledgement}
    {
    I would like to thank Dr Clarke for supervising my project and providing advice on writing F\# code and using Fable for interop with JavaScript. I would also like to thank Zaid Ajaj and Alfonso Garcia-Caro, the authors of Fable, for answering my questions on GitHub regarding Fable version issues.
    }
    
\end{columns}
 
\end{document}
